---
title: "Uk3"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
---

Here we plot the correlation matrix and the first 3 eigenvectors of Uk3.

*What is Uk3? A data set? Please briefly explain.*

```{r chunk_options, include = FALSE}
knitr::opts_chunk$set(cache = TRUE,collapse = TRUE,comment = "#",
                      fig.path = "figures/Figure3.Rmd",fig.align = "center",
                      fig.width = 8,fig.height = 6) 
```

Begin by loading these packages into your R environment.

```{r packages, message = FALSE}
library(gplots)
library(ggplot2)
library(colorRamps)
library(fields)
library(lattice)
```

**TO DO:** *Briefly explain here what this code chunk does. It looks like
it is loading the data and/or results and then generates a brief summary of 
the data in a bar chart.*

```{r load_results, fig.width = 10}
covmat = readRDS("../../Data_vhat/covmatwithvhat.rds")
z.stat = read.table("../../Inputs/maxz.txt")
names  = colnames(z.stat)
pis    = readRDS("../../Data_vhat/piswithvhat.rds")$pihat
pi.mat = matrix(pis[-length(pis)],ncol = 54,nrow = 22,byrow = T)
names  = colnames(z.stat)
colnames(pi.mat) = 
  c("ID","X'X","SVD","F1","F2","F3","F4","F5","SFA_Rank5",c(names,"ALL"))
barplot(colSums(pi.mat),main = 'WithVmat',las = 2,cex.names = 0.5)
```

**TO DO:** *Briefly explain here what this code chunk does.*

```{r corplotuk3, fig.height = 10, fig.width = 10}
k = 3
hclust.2 = function (d, method = "average", members = NULL)
  hclust(d, method, members)
x = cov2cor(covmat[[k]])
x[x < 0] = 0
colnames(x) = names
rownames(x) = names
h = read.table("../../Data/uk3rowindices.txt")[,1]
```

Now we produce the heatmap. Note that this is flipped in the paper:

```{r heatmapuk3final,fig.height = 10,fig.width = 10}
smat = (x[(h),(h)])
smat[lower.tri(smat)] <- NA
clrs <- colorRampPalette(rev(c("#D73027","#FC8D59","#FEE090","#FFFFBF",
                               "#E0F3F8","#91BFDB","#4575B4")))(64)
lat = x[rev(h),rev(h)]
lat[lower.tri(lat)] <- NA
n = nrow(lat)
levelplot(lat[n:1,],col.regions = clrs,xlab = "",ylab = "",
          colorkey = TRUE,at = seq(0,1,length.out = 64),
          scales = list(x = list(rot = 45)))
```

Now let's do the eigenplots:

```{r eigenplots, fig.height = 4, fig.cap = ""}
missing.tissues = c(7,8,19,20,24,25,31,34,37)
color.gtex = read.table("../../Data/GTExColors.txt",sep = '\t', 
                        comment.char = '')[-missing.tissues,]
k=3
vold=svd(covmat[[k]])$v;u=svd(covmat[[k]])$u
v=vold[h,]
names=names[h]
color.gtex=color.gtex[h,]
for(j in 1:3)
  barplot(v[,j]/v[,j][which.max(abs(v[,j]))],names="",cex.names = 0.5,
          las = 2,main = paste0("EigenVector",j,"Uk",k),
          col = as.character(color.gtex[,2]))
```

## Session information.

```{r info}
print(sessionInfo())
```
